Basic Model formulation

### 2014-11-20 documentation/model_formulation.Rmd
model formulation: equilibrium?

---
title: "Basic Model formulation"
author: "Florian D. Schneider"
date: "Tuesday, November 18, 2014"
output:
  pdf_document:
    fig_height: 3.5
    fig_width: 4
  html_document:
    keep_md: yes
fontsize: 12pt
geometry: margin=1.4in
csl: ../manuscript/amnat.csl
bibliography: ../manuscript/cas02.bib
---

@@

Therefore,

$$ \frac{d\rho_+}{dt} = \frac{d\rho_{+,-}}{dt} = \frac{d\rho_-}{dt} =0$$

>>>>

---
title: "Basic Model formulation"
author: "Florian D. Schneider"
date: "Tuesday, November 18, 2014"
output:
  html_document:
    keep_md: yes
  pdf_document:
    fig_height: 3.5
    fig_width: 4
fontsize: 12pt
geometry: margin=1.4in
csl: ../manuscript/amnat.csl
bibliography: ../manuscript/cas02.bib
---

@@

Therefore, we are looking for the general case of $G(\rho_+)$ where

$$ \frac{d\rho_+}{dt} = \frac{d\rho_-}{dt} = \frac{d\rho_{+,-}}{dt}  = \frac{d\rho_{+,+}}{dt} = \frac{d\rho_{-,-}}{dt}   = 0$$

Equilibrium has to fulfil

$$ \rho_0w_{0,+} = - m \rho_+ \,.$$

thus

$$  - m \rho_+ = \left( \delta \rho_+ + (1-\delta) \frac{\rho_+ - \rho_{+-} - \rho_{++} }{1 - \rho_+ - \rho_-} \right) (b - c \rho_+)(1- \rho_+ - \rho_-)  $$
